Vitis riparia LM

### 2018-11-07 V_riparia_LM.Rmd
V. riparia TAIP & SF

>>>>

We tested leaf number and shape factor for 2013.
```{r}
r_taip13_plot <- ggplot(r_13, aes(x = leaf, y = tooth.area.int.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 14, 1))
r_taip13_plot <- r_taip13_plot +labs(x = "Leaf number",
                               y = "Tooth area:internal perimeter")
r_taip13_plot
```

```{r}
r_taip13_mean_plot <- ggplot(r_taip13_mean, aes(x = leaf, y = avg.taip)) + geom_line() + theme_classic()
r_taip13_mean_plot <- r_taip13_mean_plot +labs(x = "Leaf number",
                               y = "Tooth area:internal perimeter")
r_taip13_mean_plot
```

We ran a LM for leaf number and shape factor in 2013.
```{r}
r_taip13_lm <- lm(avg.taip ~ leaf, data = r_taip13_mean)
summary(r_taip13_lm)
```

```{r}
r_taip13_seg <- segmented(r_taip13_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(r_taip13_seg)
```

```{r}
r_taip13_seg$psi
slope(r_taip13_seg)
r_taip13_fitted <- fitted(r_taip13_seg)
r_taip13_model <- data.frame(Leaf = r_taip13_mean$leaf, TAIP = r_taip13_fitted)
ggplot(r_taip13_model, aes(x = Leaf, y = TAIP)) + geom_line()
r_taip13_lines <- r_taip13_seg$psi[, 2]
r_taip13_mean_break <- r_taip13_plot + geom_vline(xintercept = r_taip13_lines, linetype = "dashed")
r_taip13_mean_break
ggsave("r_taip13_break.png")
```

We tested leaf number and tooth area:internal perimeter for 2015.
```{r}
r_taip15_plot <- ggplot(r_15, aes(x = leaf, y = tooth.area.int.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 14, 1))
r_taip15_plot <- r_taip15_plot +labs(x = "Leaf number",
                               y = "Tooth area: internal perimeter")
r_taip15_plot
```

```{r}
r_taip15_mean_plot <- ggplot(r_taip15_mean, aes(x = leaf, y = avg.taip)) + geom_line() + theme_classic()
r_taip15_mean_plot <- r_taip15_mean_plot +labs(x = "Leaf number",
                               y = "Tooth area:internal perimeter")
r_taip15_mean_plot
```

We ran a LM for leaf number and tooth area:internal perimeter in 2015.
```{r}
r_taip15_lm <- lm(avg.taip ~ leaf, data = r_taip15_mean)
summary(r_taip15_lm)
```

```{r}
r_taip15_seg <- segmented(r_taip15_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(r_taip15_seg)
```

```{r}
r_taip15_seg$psi
slope(r_taip15_seg)
r_taip15_fitted <- fitted(r_taip15_seg)
r_taip15_model <- data.frame(Leaf = r_taip15_mean$leaf, TAIP = r_taip15_fitted)
ggplot(r_taip15_model, aes(x = Leaf, y = TAIP)) + geom_line()
r_taip15_lines <- r_taip15_seg$psi[, 2]
r_taip15_mean_break <- r_taip15_plot + geom_vline(xintercept = r_taip15_lines, linetype = "dashed")
r_taip15_mean_break
ggsave("r_taip13_break.png")
```

We tested leaf number and shape factor for 2013.
```{r}
r_sf13_plot <- ggplot(r_13, aes(x = leaf, y = shape.factor)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 14, 1))
r_sf13_plot <- r_sf13_plot +labs(x = "Leaf number",
                               y = "Shape factor")
r_sf13_plot
```

```{r}
r_sf13_mean_plot <- ggplot(r_sf13_mean, aes(x = leaf, y = avg.sf)) + geom_line() + theme_classic()
r_sf13_mean_plot <- r_sf13_mean_plot +labs(x = "Leaf number",
                               y = "Shape factor")
r_sf13_mean_plot
```

We ran a LM for leaf number and shape factor in 2013.
```{r}
r_sf13_lm <- lm(avg.sf ~ leaf, data = r_sf13_mean)
summary(r_sf13_lm)
```

```{r}
r_sf13_seg <- segmented(r_sf13_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(r_sf13_seg)
```

```{r}
r_sf13_seg$psi
slope(r_sf13_seg)
r_sf13_fitted <- fitted(r_sf13_seg)
r_sf13_model <- data.frame(Leaf = r_sf13_mean$leaf, SF = r_sf13_fitted)
ggplot(r_sf13_model, aes(x = Leaf, y = SF)) + geom_line()
r_sf13_lines <- r_sf13_seg$psi[, 2]
r_sf13_mean_break <- r_sf13_plot + geom_vline(xintercept = r_sf13_lines, linetype = "dashed")
r_sf13_mean_break
ggsave("r_sf13_break.png")
```

We tested leaf number and shape factor for 2015.
```{r}
r_sf15_plot <- ggplot(r_15, aes(x = leaf, y = shape.factor)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 14, 1))
r_sf15_plot <- r_sf15_plot +labs(x = "Leaf number",
                               y = "Shape factor")
r_sf15_plot
```

```{r}
r_sf15_mean_plot <- ggplot(r_sf15_mean, aes(x = leaf, y = avg.sf)) + geom_line() + theme_classic()
r_sf15_mean_plot <- r_sf15_mean_plot +labs(x = "Leaf number",
                               y = "Shape factor")
r_sf15_mean_plot
```

We ran a LM for leaf number and shape factor in 2015.
```{r}
r_sf15_lm <- lm(avg.sf ~ leaf, data = r_sf15_mean)
summary(r_sf15_lm)
```

```{r}
r_sf15_seg <- segmented(r_sf15_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(r_sf15_seg)
```

```{r}
r_sf15_seg$psi
slope(r_sf15_seg)
r_sf15_fitted <- fitted(r_sf15_seg)
r_sf15_model <- data.frame(Leaf = r_sf15_mean$leaf, SF = r_sf15_fitted)
ggplot(r_sf15_model, aes(x = Leaf, y = SF)) + geom_line()
r_sf15_lines <- r_sf15_seg$psi[, 2]
r_sf15_mean_break <- r_sf15_plot + geom_vline(xintercept = r_sf15_lines, linetype = "dashed")
r_sf15_mean_break
ggsave("r_sf13_break.png")
```
